Simulating an Isolated Dwarf Galaxy with Energetic Feedback and Chemical Yields from Individual Stars

### 2018-03-17 main.tex
completed revisions to main text and acknowledgments

\item 
%mm3 (\textbf{Possibly remove depending on follow up}) Formation of a significant amount of H$_2$ 
     A significant amount of H$_2$ forms
through gas phase reactions with H$^-$. This dense gas is more resistive to feedback driven outflows than the less dense gas in the galaxy. This leads to high molecular gas fractions, with an H$_2$ mass comparable to that of \ion{H}{1} by the end of the simulation. This result requires further investigation to determine if this behavior is universally true of ultrafaint dwarf galaxies. See Figure~\ref{fig:ISM_evolution}.

\item Finally, we used O and N as examples to briefly demonstrate that there are discernible differences in how individual metal species are distributed within the ISM of our galaxy. These variations could be tied to differences in yield sources among elements (for example, AGB winds vs. SNe), as suggested by \cite{KrumholzTing2018}. This will be explored in more detail in future work (Emerick et. al. \textit{in prep.}).
\end{enumerate}

@@

\section*{Acknowledgements:} A.E. is funded by the NSF Graduate Research Fellowship DGE 16-44869. G.L.B. is funded by NSF AST-1312888, NASA NNX15AB20G, and NSF AST-1615955. We gratefully recognize computational
resources provided by NSF XSEDE through grant number TGMCA99S024, by the NASA High-End Computing (HEC) Program through the NASA Advanced Supercomputing (NAS) Division at Ames Research Center, Columbia University, and the Flatiron Institute. This work made significant use of many open source software packages, including \textsc{yt}, \textsc{Enzo}, \textsc{Grackle}, \textsc{Python}, \textsc{IPython}, \textsc{NumPy}, \textsc{SciPy}, \textsc{matplotlib}, \textsc{hdf5}, \textsc{h5py}, \textsc{astropy}, \textsc{Cloudy} and \textsc{deepdish}. These are the products products of a collaborative effort of many independent developers from numerous institutions around the world. Their commitment to open science has helped make this work possible. We would also like to thank the following for their advice and valuable discussions, without which this work would not have been possible: B. Cote, S. Glover, K. Hawkins, C. Hu, K. Johnston, B. O'Shea, M. Putman, B. Smith, J. Wall, and J. Wise.

>>>>

\item 
%mm3 (\textbf{Possibly remove depending on follow up}) Formation of a significant amount of H$_2$ 
     A significant amount of H$_2$ forms
through gas phase reactions with H$^-$. This dense gas is more resistive to feedback driven outflows than the less dense gas in the galaxy. This leads to high molecular gas fractions, with an H$_2$ mass comparable to that of \ion{H}{1} by the end of the simulation. This result requires further investigation to determine if this behavior is universally true of ultrafaint dwarf galaxies. (See Figure~\ref{fig:ISM_evolution}.)

\item Finally, we used O and N as examples to briefly demonstrate that there are 
%mm3 discernible 
    marked
differences in how individual metal species are distributed within the ISM of our galaxy. These variations could be tied to differences in 
%mm3 yield sources among elements
    elemental yields among different sources 
(for example, AGB winds vs. SNe), as suggested by \cite{KrumholzTing2018}. This will be explored in more detail in future work.
%mm3 (Emerick et. al. \textit{in prep.}). [only cite after submission]
\end{enumerate}

@@

\section*{Acknowledgments:} 
%mm3 [moved personal acknowledgments to the front}
We would like to thank the following for their advice and valuable discussions, without which this work would not have been possible: B. C\^ot\'e, S. Glover, K. Hawkins, C. Hu, K. Johnston, B. O'Shea, M. Putman, B. Smith, J. Wall, and J. Wise. A.E. is funded by the NSF Graduate Research Fellowship DGE 16-44869. G.L.B. is funded by NSF AST-1312888, NASA NNX15AB20G, and NSF AST-1615955. M.-M.M.L. was funded by NASA 
%mm3 [have to scare up the number still]
We gratefully recognize computational
resources provided by NSF XSEDE through grant number TGMCA99S024, by the NASA High-End Computing (HEC) Program through the NASA Advanced Supercomputing (NAS) Division at Ames Research Center, Columbia University, and the Flatiron Institute. This work made significant use of many open source software packages, including 
%mm3 [updated capitalization to that used in relevant websites]
\textsc{yt}, \textsc{Enzo}, \textsc{Grackle}, \textsc{Python}, \textsc{IPython}, \textsc{NumPy}, \textsc{SciPy}, \textsc{Matplotlib}, \textsc{HDF5}, \textsc{h5py}, \textsc{Astropy}, \textsc{Cloudy} and \textsc{deepdish}. These are products of collaborative effort by many independent developers from numerous institutions around the world. Their commitment to open science has helped make this work possible.
